{\bf \huge Wikiplia}:\\ The Free Programming Language\\ That Anyone Can Edit

### 2007-03-19 wikiplia/paper/wikiplia.tex
almost done, need screenshots

% TODO: license
\newcommand\currentrevision{465}

@@

\newcommand\wcite[1]{\footnote{\tiny Wikipedia, the free encyclopedia: {\it #1}; 2007}}
\newcommand\comment[1]{}
\newcommand\z{\ensuremath{\!}}

@@

Wikiplia, the free programming language that anyone can edit, is
implemented as a web-site on the Internet at the address
$${\tt http://wikiplia.spacebar.org/}$$

@@

\bigskip
This license is bootstrapping in the sense that it grants only the
minimal permissions necessary, after setting up invariants via the
behavior-limiting invincible sections. In fact, the original version
of the license does not directly permit the licensee to copy the
software at all; he must first amend the license using provision {\tt
VI} to give himself this permission.

@@

% All popular modern languages are defined via a definitional
% interpreter\wcite{JavaScript}\wcite{Objective Caml}\wcite{Perl} with
% accompanying O'Reilly ``animal'' book.

>>>>

\newcommand\currentrevision{475}
\newcommand\wikipliaurl{http://wikiplia.spacebar.org/}

@@

\newcommand\wcite[1]{\footnote{\tiny Wikipedia, the free encyclopedia: {\it #1}; 2007}}
\newcommand\wciteshort[1]{\footnote{\tiny Wikipedia, the free encyclopedia: {\it #1}}}
\newcommand\comment[1]{}
\newcommand\z{\ensuremath{\!}}

@@

Wikiplia, the free programming language that anyone can edit, is
implemented as a web-site on the Internet at the address
$${\tt \wikipliaurl}$$

@@

\bigskip
This license is bootstrapping in the sense that it grants only the
minimal permissions necessary, after setting up invariants via the
behavior-limiting invincible sections. In fact, the original version
of the license does not directly permit the licensee to copy the
% double-entendre with VI intentional
software at all; he must first amend the license using {\tt VI} to
give himself this permission.

@@

We have reached the end of our journey. But the journey is not
complete! We conclude with a discussion of future plans and unrelated
work, and then conclude with another paragraph.

\subsection{Future Work}

Though Wikipedia in its current form is a usable general-purpose
programming language, work remains to be done for it to reach its full
potential. For one, it needs a vibrant community of contentious and
hubristic editors hiding behind anonymous IP addresses boldly
asserting half-baked syntactic extensions or enforcing superficial
style preferences, gritting their teeth while typing and clicking
white knuckled in a kind of road rage\wcite{List of rages} created by
the dehumanizing semantic markup by which they are forced to
communicate.

% XXX: supporting users with revision #s?

We also seek to improve the languages. The language {\tt w} needs many
more features to speed development: the parenthesis-based XESP syntax
should eventually be replaced by a pleasant concrete syntax, if we can
get around to it before too much code is written in XESP. A type
system\wcite{Type system} is not planned, because type systems
restrict Freedom~\fexpression, the freedom of expression. However, we
should seek to make Wikiplia as multi-paradigm as possible (again,
freedom from discrimination on the basis of paradigm\wcite{paradigm}
orientation), supporting OOPs-oriented
programming,\z\wcite{Object-oriented programming} aspect-oriented
programming,\z\wcite{Aspect-oriented programming} duck-oriented
typing,\z\wcite{Duck typing} orientation-oriented
orienteering,\z\wcite{Orienteering} Orient-oriented
Programming,\z\wcite{The Orient} etc.

The {\tt
page} language needs extensions for developing human-readable web
pages, mostly for the purpose of creating jazzy graphics and boxes
that distract from or directly call attention to obvious problems with
the pages without actually addressing those problems.

\subsection{Unrelated Work}

All popular modern languages are defined via a definitional
interpreter\wcite{JavaScript}$^,$\wcite{Objective
Caml}$^,$\wcite{Perl} with accompanying O'Reilly ``animal''
book.\z\wcite{O'Reilly Media} The work on Wikiplia is unrelated: We
have no animal mascot\wcite{ORLY owl} and the languages are described
by a tower of source-to-source translations on top of a universally
parseable semantic document in XML\wciteshort{Category:ML programming
language family} form.

The author doesn't think much of musicals,\z\wcite{Musical theatre} to
be perfectly\wcite{Thomas Aquinas} honest,\z\wcite{Honesty} so those
are basically a no-go. He also feels that the metric
system\wcite{Metric system} and time zones\wcite{Time zone} are pretty
overrated. Ketchup\wcite{Ketchup} on eggs\wcite{Egg (food)} is
gross,\z\wcite{Gross} but not quite as gross as foie gras\wcite{Foie
gras}, which more or less has the word ``gross'' in its name so
duh.\z\wcite{Duh}

\subsection{Another Paragraph}

We have described Wikiplia, the free programming language that anyone
can edit. Unlike other programming languages, it is designed to
support a variety of freedoms (\ftinker, \fexpression, \fbeer, \fusa,
\ffree, \ftobe) and is explicitly scalable to new freedoms. The system
is implemented in a minimal bootstrapping core, and then built up to
a featured system using its own faculties for extension. XXX more...

\bigskip
$${\tt \wikipliaurl}$$
